---
title: "fix_sediments"
author: "Ouida"
date: "15 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Set up the packages
```{r}
## install individual packages when there are issues with tidyverse
# install.packages('readr')
# install.packages('dplyr')
# install.packages('tidyr')
# install.packages('janitor')
# install.packages('lubridate')

## load individual packages
library(readr)
library(dplyr)
library(tidyr)
library(janitor)
library(lubridate)
```
Load the data
Sediments dataset accessed directly at the Zenodo repository. Data citation:
Ritson-Williams, R., and Gates, R. D. (2016). Kaneohe Bay Sediment Data 2015 [Data set]. Zenodo. http://doi.org/10.5281/zenodo.61137

```{r}
sediments_raw <- read_csv("https://zenodo.org/record/61137/files/Kbay_sediment_2015.csv")
head(sediments_raw)
```

Make a reef column with consistent site labels
```{r}
## clean headers and reef record names
sediments <- clean_names(sediments_raw)
sediments <- sediments %>%
  mutate(reef = gsub("reef", "reef_", site)) %>%
  mutate(reef = gsub("HIMB", "reef_himb", reef))
```

Check that dates are in proper YYYY-MM-DD format and convert to new year_month column
```{r}
## note that loading dataset with read.csv formatted dates as factors
## therefore loaded dataset with read_csv instead to format dates as Date
## assign year_month to align with monthly datasets
sediments <- sediments %>%  
 # mutate(date_formatted = as.Date(date,'%Y-%m-%d')) ## not needed since dates are in ISO 8601 format already
  mutate(year_month=floor_date(date ,unit="month")) %>%
  arrange(.data$reef, .data$year_month, .data$sediment_grams_per_day, .data$date)
head(sediments)
```

Select and order columns for inspection before creating summary monthly dataset
```{r}
## have chosen here to retain original sampling date in sediments but drop from monthly summary
sediments <- sediments %>%
  select(.data$reef, .data$year_month, .data$sediment_grams_per_day, .data$date)
head(sediments)
```

Find monthly means and drop sampling date column
```{r}
sediments_monthly <- sediments %>% 
  group_by(reef, year_month) %>%
  summarise(sediment_mean_grams_per_day=mean(sediment_grams_per_day)) %>% 
  ungroup() 
sediments_monthly
```

Save the new file
```{r}
write_csv(sediments_monthly,"data_tidy/sediments_monthly.csv")
```
