---
title: "Light"
author: "Leslie & Cheryl"
date: "March 14, 2018"
output: html_document
---

## Load libraries and data
```{r setup, echo = TRUE, message = FALSE, warning = FALSE}
library(tidyverse)  # install.packages('tidyverse')
library(lubridate)  # install.packages('lubridate')  # date manipulation
library(tibbletime) # install.packages('tibbletime') # time series
```

Load 7 light (PAR) datasets from Reef 25, 42, 44 and HIMB in Kaneohe Bay between 2014-2015

```{r load data, message = FALSE, warning = FALSE}
light_reef_44_2014 <- read_csv("https://www.zenodo.org/record/160214/files/light_reef44_2014.csv")
light_reef_44_2015 <- read_csv("https://www.zenodo.org/record/160214/files/light_reef44_2015.csv")
light_reef_25_2015 <- read_csv("https://www.zenodo.org/record/160214/files/light_reef25_2015.csv")
light_reef_42_2014 <- read_csv("https://www.zenodo.org/record/160214/files/light_reef42_2014.csv")
light_reef_42_2015 <- read_csv("https://www.zenodo.org/record/160214/files/light_reef42_2015.csv")
light_reef_himb_2014 <- read_csv("https://www.zenodo.org/record/160214/files/light_reefHIMB_2014.csv")
light_reef_himb_2015 <- read_csv("https://www.zenodo.org/record/160214/files/light_reefHIMB_2015.csv")
```

## Wrangle Data
Add identifying column to denote which reef the light data came from

```{r rename columns}
light_reef_25_2015 <- mutate(light_reef_25_2015, reef = "reef_25")
light_reef_42_2015 <- mutate(light_reef_42_2015, reef = "reef_42")
light_reef_42_2014 <- mutate(light_reef_42_2014, reef = "reef_42")
light_reef_44_2014 <- mutate(light_reef_44_2014, reef = "reef_44")
light_reef_44_2015 <- mutate(light_reef_44_2015, reef = "reef_44")
light_reef_himb_2014 <-  mutate(light_reef_himb_2014, reef = "reef_himb")
light_reef_himb_2015 <-  mutate(light_reef_himb_2015, reef = "reef_himb")
```

Create a single data frame for light data from all 4 reefs

```{r bind dli all reefs}
light_all <- bind_rows(list(light_reef_25_2015,light_reef_42_2014,light_reef_42_2015, light_reef_44_2014, light_reef_44_2015, light_reef_himb_2014, light_reef_himb_2015))
```

Calculate daily light integral (dli). First, group by reef and day. Second, take the daily mean of light and convert PAR from umol/m^2/s to mol/m^2/day. To do this, multiply by 0.0864. (1 µmol m-2 s-1 = 0.0864 mol m-2 d-1)

```{r convert units}
light_dli <- light_all %>%
  group_by(reef, date) %>%  # group by reef and day
  summarize(dli = mean(`PAR_calibrated_umol/m^2/s`*0.0864, na.rm=T)) %>% # remove na's and convert units
  ungroup()

head(light_dli)
```
Create monthly light product
```{r create monthly product}
dli_monthly <- light_dli %>%
  group_by(reef, month = month(date), year = year(date)) %>%
  summarise(dli_month_mean = mean(dli), 
            dli_month_min = min(dli), 
            dli_month_max = max(dli),
            dli_month_var = var(dli))    %>%
  ungroup() %>%
  mutate(date = as.Date(paste(year, month, "01", sep = "-"), 
                        format = "%Y-%m-%d")) %>%   # add correct date format
  select(date, reef,                   
         dli_month_mean, 
         dli_month_min, 
         dli_month_max, 
         dli_month_var) # select and reorder columns

head(dli_monthly)
```
Write data frame to .csv file
```{r write csv}
write_csv(dli_monthly, "data_tidy/dli_monthly.csv", na = "NA", append = FALSE)
```

## Plot daily light across all reefs
```{r plot, message = FALSE, warning = FALSE}
rolling_mean <- rollify(mean, window = 7) # 7-day rolling mean of dli data

light_dli %>%
  mutate(mean_7 = rolling_mean(dli)) %>% # add rolling mean col to dataframe
  group_by(reef) %>%
  ggplot(aes(x = date)) + # plot date on x-axis
  geom_line(alpha = .3, aes(y = dli, color = reef)) + # plot daily means
  geom_line(size = 1, aes(y = mean_7, color = reef)) + # plot 7d smoothed
  labs(title = "Daily Light (7 day rolling mean)", x = "Date", y = "DLI (mol m-2 d-1)")
```

Cheryl's notes for tomorrow about how to summarize light and temp: Average daily range, monthly mean, monthly max, monthly min, DHW, DHM



